\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[usenames,dvipsnames]{color}

\pagestyle{empty}
\geometry{letterpaper,tmargin=0.75in,bmargin=0.75in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=0in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0.1in}
\setlength{\itemsep}{-0.2cm}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\newcommand{\bigsection}[1]{	
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}

%	\vspace{-10pt} \rule{\textwidth}{1pt}
}

\newcommand{\microns}{$\mu m$}

\begin{document}

\fontfamily{ppl}\selectfont

\bigsection{Responsibilites to research group before I leave: \textbf{\textit{Progress So Far}}}

\textbf{Tasks in progress}
\begin{itemize}

\item \textbf{Masters Thesis:} Determined structure of thesis, laid out table of contents. Detailed notes on contents completed; 
see attached.

\item \textbf{Silica samples for new postdoc:} Liz + Ekandrea.

\item \textbf{My part of Willie's paper:} Done.
%: recheck all the math and code for the diffusion analysis, recheck text in paper.

\item \textbf{Nuzzo collaboration:} Scott is working on new draft for resubmission. I'm keeping involved in this as much as I can.

\item \textbf{Confocal microscope repair:} After additional conversations with Steve at Visitech, have determined that the piezo 
controller is at fault.  Visitech does not manufacture this component, but instead obtains it from Physik Instruments. Visitech is
handling the repair of the controller by PI on their end.

\end{itemize}

\textbf{Knowledge transfer}
\begin{itemize}

\item \textbf{Documentation of 81ESB fluorescence:} Partially done.

\item \textbf{SFL training + docs:} Good progress on training Steve. (Have not yet begun with John due to scheduling.) Docs not yet
written, but plan to use combination of my notes + Steve's notes to produce these.

\item \textbf{Confocal training + docs:} Have been waiting on confocal repairs; may have to begin training sooner. Group jobs have
assigned this to Steve. Jaci docs exist but still must be updated.

\item \textbf{Zetasizer:} Scheduled training for maintenance with Brett for next week.

\item \textbf{Wiki:} Transferred admin access + training to Steve.

\item \textbf{Particle tracking software:} Organized program files, not yet written docs. This for Gao?

\item \textbf{Train for clean-room master fabrication:} Waiting on Steve and John's cleanroom authorization.

\end{itemize}

\textbf{Lab maintenance}
\begin{itemize}

\item \textbf{SFL microscope in top condition:} Have ordered new supplies for microscope + SFL. Scheduling Olympus service visit with John.

\item \textbf{Confocal microscope in top condition:} Have ordered new supplies. Waiting on piezo.

\item \textbf{Clean and re-organize my lab space:} Not yet done.

\item \textbf{Disposition of chemicals:} Transferred essentials for SFL, fluorescent dyes, etc. to Steve. Misc chemicals to be collected in
waste pickup.

\end{itemize}

\pagebreak

\bigsection{Explanation of Thesis Outline}

The attached thesis outline is based on the Physics Dept LaTeX template for a UofI graduate thesis. I have
attached a proposed table of contents, and an outline of each chapter which contains sections and short 
bullet-point summaries.  The bullet points represent a ``first best guess'' at the contents of each section:
ideally, I should be able to go through this document and replace every one-three bullets with a paragraph.
Figures I plan to slot into each chapter are also listed.

\textbf{The bullet points are color-coded:}\\
\textcolor{BrickRed}{Red text represents incomplete experimental or analytic work.}\\
\textcolor{Green}{Green text represents experiments or analysis which are already complete.}\\
Black text represents background or explanatory text to be inserted.

I currently plan to begin writing with the sections for which there is no incomplete labwork. I will start with the
introduction and literature review, followed by the chapters on ``exotic'' particles and tracking algorithms for which
no new experimental work is planned. I have the chapter on rods placed later in my schedule (late September) so that
I can ensure no new experimental work is required first.  The appendices are last given their lower priority.

\end{document}