\chapter*{Acknowledgments}

The completion of this work involved the participation of many 
talented scientists and engineers in addition to myself,
and without their assistance I would still be sitting perplexed in the lab.  

First of all I would like to thank my advisor, Professor Jennifer 
Lewis, whose contributions and support were essential at all 
stages of this project.  Professor Jacinta Conrad and Dr. Robert
Shepherd also provided essential assistance throughout my 
entire graduate career, contributing valuable knowledge and 
suggestions both in the lab and with my data analysis.  I owe
special thanks to my undergraduate assistants, Alissa Cote,
Stephen Menke, Fatima Salazar, and Kundan Chaudhary, who collectively 
fabricated and imaged many thousands of interestingly-shaped particles
and provided many helpful ideas.  I had many helpful conversations
with Scott Slimmer, who was also kind enough to proofread this
document.  I would also like to thank 
the rest of the Lewis Group for their help and support in more ways than
I can count; and in particular, Elizabeth Glogowski, Chris Hansen, John
Vericella, David Lorang, Willie Wu, and Steve Kranz.  Special thanks also go to Jon
Ekman of the Imaging Technology Group at the Beckman Institute, who
assisted in acquiring many of the images used in the analysis of Janus
assembly in Chapter 3 and is now enjoying sunny Florida.

My thanks and appreciation go to the University of 
Illinois, the Army Research Office, and 
the American Society for Engineering Education, who provided
funding and support throughout my graduate career.

I would also like to convey my personal thanks to my friends and 
family, who reminded me that there is more to life than research.
Mom, Dad and Brian were always there for me, and had to listen to me rant
about frustrations in the lab far more often than I like to admit.
Dr. Huaibin Zhang was kind enough to give me fascinating things
to work on while I wasn't worrying about Janus particles, and Max,
Steve, and Phil gaves me games to play when I was done with that, too.
Dorian, Moki and Tink were all true friends during rough times and 
deserve their own share of credit for the completion this work.
And most of all I thank Leigh, without whom I would still be 
utterly lost, hiding in a lab.  This is for you.
